Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimization Choices

### 2025-11-21 jso.tex
small tweaks

\begin{tcolorbox}[enhanced jigsaw, breakable, bottomtitle=1mm, opacitybacktitle=0.6, toptitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm, colbacktitle=quarto-callout-note-color!10!white, opacityback=0, toprule=.15mm, left=2mm, bottomrule=.15mm, rightrule=.15mm, titlerule=0mm, coltitle=black, leftrule=.75mm, colframe=quarto-callout-note-color-frame, colback=white]

>>>>

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, coltitle=black, opacitybacktitle=0.6, title={Algorithm: Jellyfish Optimizer Pseudo Code}, breakable, opacityback=0, toprule=.15mm, left=2mm, bottomtitle=1mm, rightrule=.15mm, bottomrule=.15mm, titlerule=0mm, colframe=quarto-callout-note-color-frame, colback=white, leftrule=.75mm, toptitle=1mm]
